A nice acyclic matching on the nerve of the partition lattice

### 2019-01-31 paper3/equivariant.tex
linear sum -> ordinal sum

For an order-preserving map with small fibers $\varphi$ let $M(\varphi)$ denote its associated acyclic matching which consists of all fibers of cardinality $2$, see \cite[Chapter 11]{buch}.
\begin{prop}
Let $G$ be a group acting on a finite poset $P$. For any order-preserving $G$-map $\varphi:P\longrightarrow Q$ with small fibers, the acyclic matching $M(\varphi)$ is $G$-equivariant. On the other hand, any $G$-equivariant acyclic matching $M$ on $P$ can be represented as $M=M(\varphi)$, where $\varphi:P\longrightarrow Q$ is an order-preserving $G$-map with small fibers.
\end{prop}
For two disjoint posets $(P_1,\leq_{P_1})$, $(P_2,\leq_{P_2})$ let $P_1\oplus P_2$ denote the linear sum of $P_1$ and $P_2$, where the set of $P_1\oplus P_2$ is $P_1\cup P_2$ and for two elements $x,y\in P_1\cup P_2$ we set $x\leq y$ if one of the following three conditions is satisfied:
\begin{enumerate}
\item $x,y\in P_1$ and $x\leq_{P_1} y$
\item $x,y\in P_2$ and $x\leq_{P_2} y$
\item $x\in P_1$ and $y\in P_2$
\end{enumerate}
Furthermore if a group $G$ acts on $P_1$ and on $P_2$, then we obtain a canonical action of $G$ on $P_1\oplus P_2$.
\begin{proof}
The first statement is easy to see. Assume we are given an $G$-equivariant acyclic matching $M$ on $P$.

>>>>

For an order-preserving map with small fibers $\varphi$ let $M(\varphi)$ denote its associated acyclic matching which consists of all fibers of cardinality $2$, see \cite[Chapter 11]{buch}.
\begin{prop}
Let $G$ be a group acting on a finite poset $P$. For any order-preserving $G$-map $\varphi:P\longrightarrow Q$ with small fibers, the acyclic matching $M(\varphi)$ is $G$-equivariant. On the other hand, any $G$-equivariant acyclic matching $M$ on $P$ can be represented as $M=M(\varphi)$, where $\varphi:P\longrightarrow Q$ is an order-preserving $G$-map with small fibers.
\end{prop}
For two disjoint posets $(P_1,\leq_{P_1})$, $(P_2,\leq_{P_2})$ let $P_1\oplus P_2$ denote the \emph{ordinal sum}\footnote{Called \emph{stack} in \cite{buch}} of $P_1$ and $P_2$, where the set of $P_1\oplus P_2$ is $P_1\cup P_2$ and for two elements $x,y\in P_1\cup P_2$ we set $x\leq y$ if one of the following three conditions is satisfied:
\begin{enumerate}
\item $x,y\in P_1$ and $x\leq_{P_1} y$
\item $x,y\in P_2$ and $x\leq_{P_2} y$
\item $x\in P_1$ and $y\in P_2$
\end{enumerate}
Furthermore if a group $G$ acts on $P_1$ and on $P_2$, then we obtain a canonical action of $G$ on $P_1\oplus P_2$.
\begin{proof}
The first statement is easy to see. Assume we are given an $G$-equivariant acyclic matching $M$ on $P$.
